Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
Placeholders

% Packages for bold math
\usepackage{bm}
\newcommand{\mathbold}[1]{\bm{#1}}
\newcommand{\mbf}[1]{\mathbf{#1}}

@@

\section{Sparse Function-space Sequential Learning}

@@

\subsection{Sparse functional regularization (SFR) in Continual learning}
% Definition of CL -> a sequence of tasks 
% Possible storyline:
after each task we use the model

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/img_super.tex}
\end{table}

@@

\section{Discussion and Conclusion}
\label{sec:conclusion}

@@

\section{Method Details}

Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

\section{Model-based Reinforcement Learning}
\label{sec-rl-appendix}

@@

\section{Extending the CL regularizer to multi-class settings}
\begin{equation}
	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
\end{equation}

>>>>

% Packages for bold math
\usepackage{bm}
\newcommand{\mathbold}[1]{\bm{#1}}
\newcommand{\mbf}[1]{\mathbf{#1}}
\renewcommand{\mid}{\,|\,}

@@

\section{Sparse function-space sequential learning}

@@

\subsection{Sparse functional regularization (SFR) in continual learning}
% Definition of CL -> a sequence of tasks 
% Possible storyline:
after each task we use the model

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	%\input{tables/img_super.tex}
\end{table}

@@

\section{Discussion and conclusion}
\label{sec:conclusion}
%

@@

This supplementary document is organized as follows. 
%
\cref{app:method} provides a more extensive overview of the techncical details of \our.
%
\cref{app:cl} covers the sparse-functional regularisation (SFR) setup for continual learning.
%
\cref{app:rl} provides a more extensive writeup of the reinforcement learning setup used in the experiments.
%
\cref{app:experiments} provides the full details of each individual experiments in the main paper.

\section{Method details}
\label{app:method}
%
Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

\section{Sparse functional regularisation in continual learning}
\label{app:cl}

\subsection{Extending the CL regularizer to multi-class settings}
\begin{equation}
	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
\end{equation}

\section{Sparse functional model-based reinforcement learning}
\label{app:rl}

@@

\section{Experiment details}
\label{app:experiments}

\subsection{Uncertainty quantification on UCI data sets}
\label{app:uci}

\subsection{Uncertainty benchmarks for image data}
\label{app:image}

\subsection{Sparse functional regularisation in continual learning}
\label{app:cl-experiment}

\subsection{Reinforcement learning experiment}
\label{app:rl-experiment}
